R works, of course.

```{r}
#| label: test-r
#| engine: R
library(knitr)
set.seed(123)
rnorm(5)
```

Does **knitr** work with Python? Use the chunk option `engine='python'`:

```{r}
#| label: test-python
#| engine: python
x = 'hello, python world!'
print(x)
print(x.split(' '))
```

Or use the syntax ```` ```{python} ````:

```{python}
x = 'hello, python world!'
print(x.split(' '))
```

If all the chunks below are python chunks, we can set the engine globally:

```{r}
#| label: setup
#| include: false
opts_chunk$set(engine = 'python')
```

## Chunk Options

You can use some chunk options like `eval`, `echo` and `results`. For example, `eval=FALSE` (do not evaluate code):

```{r}
#| label: test-eval
#| eval: false
#| ref.label: test-python
```

or `echo=FALSE` (hide source code):

```{r}
#| label: test-echo
#| echo: false
#| ref.label: test-python
```

or `results='hide'`:

```{r}
#| label: test-hide
#| results: hide
#| ref.label: test-python
```

or `results='asis'`:

```{r}
#| label: test-asis
#| results: asis
print('**Write** _something_ in `Markdown` from `Python`!')
```

You can also cache the computation:

```{r}
#| label: test-cache
#| cache: true
import time
# pretend this is a time-consuming task...
time.sleep(10)
print(1+1)
```

## Strict Markdown

You can use strict markdown (i.e. indent by 4 spaces) by setting `render_markdown(TRUE)`.

```{r}
#| label: strict-markdown
#| engine: R
render_markdown(TRUE)
```

Now see how the output is changed:

```{r}
#| label: test-py-again
#| ref.label: test-python
```
