# Using CoffeeScript with knitr

First we set a flag `-p` for the `coffee` engine to print the JavaScript output instead of evaluating the code (`engine.opts = '-p'`):

```{r}
#| label: setup
#| include: false
knitr::opts_chunk$set(cache = TRUE, engine.opts = '-p')
```

You need to install `coffee`, the command-line version of [CoffeeScript](http://coffeescript.org/#installation).

CoffeeScript compiles javascript:

```{r}
#| label: square_function
#| engine: coffee
#| comment: //
@square = (x) -> x * x
```

To use CoffeeScript in an HTML document, use `results="asis"`, `echo=FALSE`, and wrap the chunk in `<script>` tags.

```{r}
#| ref.label: math_functions
#| engine: coffee
#| eval: false
```
```{r}
#| ref.label: call_math
#| engine: coffee
#| eval: false
```

<script type="text/javascript">
```{r}
#| label: math_functions
#| engine: coffee
#| results: asis
#| echo: false
@square = (x) -> x * x
@cube   = (x) -> square(x) * x
```

```{r}
#| label: call_math
#| engine: coffee
#| results: asis
#| echo: false
p = document.createElement("p");
p.appendChild(document.createTextNode("The cube of 3 is " + cube(3)))
document.body.appendChild(p)
```
</script>

Of course you can also run the code, if you remove the `-p` flag from the chunk option `engine.opts` (I'm not evaluating this code chunk here because I do not have a proper version of `coffee` on Debian yet; if you do, you can remove `eval=FALSE`):

```{r}
#| engine: coffee
#| engine.opts: ''
#| eval: false
x = 42
console.log "The answer is ", x
```
