# Different cache levels
```{r}
#| label: init
#| cache: 0.0
#| echo: false
# Work around issue #645 in knitr
library(methods)
```
`cache=FALSE` or `cache=0` means no cache:

```{r}
#| label: test-cache-a
#| cache: 0.0
Sys.sleep(1)
1 + 1
plot(cars)
```

`cache=1` means to save the results from `evaluate::evaluate()`, and pretend
the code has been evaluated; all the output hooks will be applied every time
the document is recompiled; note the plots are also saved as display lists,
and will be redrawn every time the document is recompiled:

```{r}
#| label: test-cache-b
#| cache: 1.0
#| ref.label: test-cache-a
```

`cache=2` is similar to `cache=1`, and the only difference is that the plots
will not be redrawn, in which case you need to make sure you did not delete
the figure files manually:

```{r}
#| label: test-cache-c
#| cache: 2.0
#| ref.label: test-cache-a
```

`cache=TRUE` or `cache=3` means to cache the text output of a chunk; none of
the output hooks will be called when the document is recompiled, and the
plots will not be redrawn, either:

```{r}
#| label: test-cache-d
#| cache: 3.0
#| ref.label: test-cache-a
```

Below is a test case for [#588](https://github.com/yihui/knitr/issues/588):

```{r}
#| label: test-cache-e
#| cache: 2.0
#| fig.width: 30.0
#| fig.height: 30.0
pairs(matrix(rnorm(100), ncol=100), labels=1:100, pch='.')
```

Another test case, with more plots:

```{r}
#| label: test-cache-f
#| cache: 2.0
Sys.sleep(5)
plot(1:10)
abline(0, 1)
plot(2:11)
```
